\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-15 paper.tex
merged sections 3 and 5
changing the order of institutions to alphabetical

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\star$Microsoft, $^\diamond$Massachusetts Institute of Technology\\
} % end author

@@

\section{Testing Distributed Systems}
\label{sec:overview}

@@

\section{The \psharp Systematic Testing Engine}
\label{sec:psharp}

\input{psharp}

>>>>

%for single author (just remove % characters)
\author{
{\rm Pantazis Deligiannis$^\dagger$, Matt McCutchen$^\diamond$, Paul Thomson$^\dagger$, Shuo Chen$^\star$}\\
{\rm Alastair F. Donaldson$^\dagger$, John Erickson$^\star$, Cheng Huang$^\star$, Akash Lal$^\star$}\\
{\rm Rashmi Mudduluru$^\star$, Shaz Qadeer$^\star$, Wolfram Schulte$^\star$}\\\\
$^\dagger$Imperial College London, $^\diamond$Massachusetts Institute of Technology, $^\star$Microsoft\\
} % end author

@@

\section{Our Approach to Testing Distributed Systems}
\label{sec:overview}

@@

%% \section{The \psharp Systematic Testing Engine}
%% \label{sec:psharp}
%% \input{psharp}
